\chapter{Introduction}\label{ch:intro}
%these sections are optional, up-to the author
\section{Motivation}
\hspace{7mm}In this case connection of two sides is most important. Potential customers , especially old generation is suffering from having troubles with technical moments that includes household chores as everyday technologies are developing , and many people in our country just don’t have opportunity to follow everything. Every day we see how technologies for out day life that were basic for people , is being more digitalized(examples like refrigerator or vacuum cleaner). Moreover other problems like to build something had always been problem for people , finding someone who can do it , seeing their reviews and location to take it less time was always an enormous problem. Day by day issues like delivery of food and etc were in the same category , however in Kazakhstan we can see progress in those spheres. Applications like Wolt or Glovo are being in high demand , and their companies are also getting good reputation in market.


For good specialists is hard to work efficiently and being needed for society , as alternatives where they try to find work to do are not respected by community or have not good conditions so they can’t work for their benefit. Having opportunity to find costumers in their area , that will save time for travel , and doing it in application that focuses only in that area will motivate them to do their best and help other people.


Our society is still priorities time and will do everything not to do household chores. It will give them chance to focus on their problems they have and cancel the issue which was destructing them. It will create more communication with specialists and faith in digitalization that our country needs to become more progressive country. Especially old generation by having good experience with our service will start more on believing that digitalization is something good to have and to know.
\section{Aims and Objectives}
\hspace{7mm}Providing chance to socialize and giving believe in good specialists in the country will provide our community to be more progressive which will lead to increase interest in applications that provides service. We already being in step where application like our is being in charts , and mostly everyone already cannot life without them. However it's mostly international companies , and problem of not having faith in things our nation can do still exist. Our project aim is to provide very comfortable application with great design , which is very important to mention as it is one of the most important things costumer notice while opening the application for their first time , and of course with great technical part that will try to minimize technical problems. 
Also important to provide our specialist with great experience who can help community with their knowledge. Our project target to give them the chance to work efficiently in sphere they like , and minimize household problems for citizens. Those specialists suffer from not having good enough application in the country as they cannot earn money as they deserved to.


Customers to get more time on their work is important. Moreover we try to gain their respect so they will believe that applications made by our nation are good enough , specialists in our country are pleasant and clever. It will literally give us the meaning to work. Our country in this sphere isn't developed enough, applications that we have aren’t spread across the country and have no alternatives to compete with. Competition is creating of progress in the market , and one more motivation to be better every day and by that our society will gain more quality service , more specialists will try to be professional to give their service and earn money , and sphere in our country will developed more and more


For our country it will also give more congeniality with big countries as all technologies will be more and more in interests as they won’t be no more scary our nation. Every time we will advertise out application , people will know while choosing to get something , that they can always make it in our application


Problems with household chores were always and everywhere. It's always hard to understand in every sphere we have and use every day, that is why when something breakes at homes it's usually ignored as people mint not to believe to specialist in companies as they think cost for their work is too overpriced. Our project aims to break that believe and give customers fair pay for work.
\section{Thesis Outline}
\hspace{7mm}Purpose of the work is to give opportunity for specialists to work and do their best for our citizens. Our project will give them opportunity to show themselves and having chance to work in good conditions.


Costumers will have fast and good-quality service which in the future will be developing. They will solve their problems as fast as it can be , and will have less problems that may prevent them from real problems


Our case is win - win for both sides where customers can have opportunity to order specialists in nearby location to help them with the problem they accrued , and save their time. Specialists will get opportunity to work in great conditions , and we know that by finding job it is one of the most important point that workers priorities.
